Adding selection to \stdpopsim: oh how the tables have turned

### 2024-05-29 analysis2_manuscript.tex

    As with other \stdpopsim models, we aim to hew as closely as possible
    to realistic genomes, and provide public annotations of specices-specific functional
    elements that can be used along with a \texttt{DFE} object to
    readily provide realistic model of selection for a specific genome and set of
    populations. 
    % A figure here would be great to show how this works

@@

\section*{Additions to stdpopsim}
    \label{additions}

>>>>

    \begin{figure}[t!]
        \centering
        \includegraphics[width=0.2\textwidth]{figures/schematics/catalog.pdf}
        \caption{
        \label{fig:schematic}
        A schematic of the \stdpopsim catalog for simulating genetic variation
        in a population. The user specifies a species, a portion of the genome to simulate,
        and optionally a genetic map, a model of demography, and a model of selection that 
        itself is composed of a distribution of fitness effects (DFE) and a set of functional
        annotations.
        }
    \end{figure}

    As with other \stdpopsim models, we aim to hew as closely as possible
    to realistic genomes, and provide public annotations of specices-specific functional
    elements that can be used along with a \texttt{DFE} object to
    readily provide realistic model of selection for a specific genome and set of
    populations. A schematic of the \stdpopsim catalog is shown in Figure \ref{fig:schematic}.
    From a users perspective, one can specify a species, a portion of the genome to simulate,
    a genetic map if available, a model of demography, and a model of selection that is
    composed of a set of annotations and a \texttt{DFE} object.

    While the vast majority of published DFE estimates are based on a limited number of species,
    in particular humans and \textit{Drosophila}, these are mix and match with the other species
    in the catalog. For instance, one could simulate a butterfly species with a Gamma DFE originally
    estimated from humans, or a human population with a DFE estimated from \textit{Drosophila}.

@@

\section*{Example applications}
    \label{additions}
